Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-26 writing/DraftExposurePaper/DraftExposurePaper.Rmd
code with county_timeseries function

```{r echo = FALSE, fig.width = 5.5, fig.height = 4}
compare_rain %>% group_by(fips) %>%
        summarize(ave_rain_mm = mean(rain_mm),
                  ave_tot_precip = mean(tot_precip),
                  n = n(),
                  within_500_km = first(storm_dist) <= 500) %>%
        ggplot(aes(x = ave_tot_precip, y = ave_rain_mm, 
                   size = n, color = within_500_km)) + 
        geom_hline(yintercept = 75, color = "gray") + 
        geom_vline(xintercept = 75, color = "gray") + 
        geom_point(alpha = 0.5) + 
        theme_bw() +
        xlim(c(10, 225)) + ylim(c(10, 225)) + 
        geom_abline(intercept = 0, slope = 1) + 
        xlab("Rainfall based on NLDAS-2 data (mm)") + 
        ylab("Rainfall reported in Monthly \nWeather Report (mm)")  + 
        scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "black"), 
                           guide = "none") 
```

```{r echo = FALSE, fig.height = 4, fig.width = 6}
allison_gauge <- read.csv("MWR_gauge_rain_data/allison_mwr.csv")
allison_nldas <- county_rain(counties = unique(allison_gauge$fips),
                             start_year = 2001, end_year = 2001,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
allison_nldas <- allison_nldas %>%
        filter(storm_id == "Allison-2001")
allison_gauge$fips <- as.character(allison_gauge$fips)
compare_rain <- right_join(allison_nldas, allison_gauge, by = "fips")
#alex_nldas <- as.data.table(alex_nldas)
#alex_gauge <- as.data.table(alex_gauge)
#compare_rain <- left_join(alex_nldas, alex_gauge, by = "fips")
a <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw()
a
```

```{r echo = FALSE, fig.width = 5.5, fig.height = 4}
compare_rain %>% group_by(fips) %>%
        summarize(ave_rain_mm = mean(rain_mm),
                  ave_tot_precip = mean(tot_precip),
                  n = n(),
                  within_500_km = first(storm_dist) <= 500) %>%
        ggplot(aes(x = ave_tot_precip, y = ave_rain_mm, 
                   size = n, color = within_500_km)) + 
        geom_hline(yintercept = 75, color = "gray") + 
        geom_vline(xintercept = 75, color = "gray") + 
        geom_point(alpha = 0.5) + 
        theme_bw() +
        xlim(c(25, 200)) + ylim(c(25, 800)) + 
        geom_abline(intercept = 0, slope = 1) + 
        xlab("Rainfall based on NLDAS-2 data (mm)") + 
        ylab("Rainfall reported in Monthly \nWeather Report (mm)") + 
        scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "black"), 
                           guide = "none") 
```

@@

```{r}
#devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
#devtools::install_github("leighseverson/countyweather")
library(countyweather)
options("noaakey" = Sys.getenv("noaakey"))
#Alex-2010
alex_fips <- alex_nldas$fips
alex_fips <- unique(alex_fips)
#alex_weather <- weather_fips(fips = alex_fips,
                             #date_min = "2010-06-25",
                             #date_max = "2010-07-02",
                             #var = "PRCP") # Returns warning: "sorry, no data found"
                                            # and problemin station_ids$meta . . .
#Ike-2008
ike_fips <- ike_nldas$fips
ike_fips <- unique(ike_fips)
#ike_weather <- weather_fips(fips = ike_fips,
                             #date_min = "2008-09-01",
                             #date_max = "2010-09-14",
                             #var = "PRCP") # Same thing here
```

>>>>

```{r echo = FALSE, fig.width = 5.5, fig.height = 4}
compare_rain %>% group_by(fips) %>%
        summarize(ave_rain_mm = mean(rain_mm),
                  ave_tot_precip = mean(tot_precip),
                  n = n(),
                  within_500_km = first(storm_dist) <= 500) %>%
        ggplot(aes(x = ave_tot_precip, y = ave_rain_mm, 
                   size = n, color = within_500_km)) + 
        geom_hline(yintercept = 75, color = "gray") + 
        geom_vline(xintercept = 75, color = "gray") + 
        geom_point(alpha = 0.5) + 
        theme_bw() +
        xlim(c(10, 225)) + ylim(c(10, 225)) + 
        geom_abline(intercept = 0, slope = 1) + 
        xlab("Rainfall based on NLDAS-2 data (mm)") + 
        ylab("Rainfall reported in Monthly \nWeather Report (mm)") + 
        scale_color_manual(values = c("blue", "black"), guide = "none") 
```

@@

```{r}
#devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
#devtools::install_github("leighseverson/countyweather")
library(countyweather)
options("noaakey" = Sys.getenv("noaakey"))
#Alex-2010
alex_fips <- alex_nldas$fips
alex_fips <- unique(alex_fips)
#alex_weather <- weather_fips(fips = alex_fips,
                             #date_min = "2010-06-25",
                             #date_max = "2010-07-02",
                             #var = "PRCP") # Returns warning: "sorry, no data found"
                                            # and problemin station_ids$meta . . .
#Ike-2008
ike_fips <- ike_nldas$fips
ike_fips <- unique(ike_fips)
#ike_weather <- county_timeseries(fips = ike_fips,
                                 #date_min = "2008-09-01",
                                 #date_max = "2008-09-14",
                                 #out_directory = paste0("/Users/joshuaferreri/",
                                                        #"Documents/ike_timeseries"),
                                 #out_type = ".csv")
```
